---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  #fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# ebaypi

## Overview

ebaypi is a wrapper package for the eBay Developer API. It helps streamline the import of listing information from active and completed eBay listings.

The core functionality focuses on the "Finding API" which is for importing listing information:

  * `search_ebay()` import data for active or completed listings from eBay


This package requires that the user has an eBay Developers account and an eBay AppId (token).  Go to the [eBay Developer](https://developer.ebay.com/) page to sign up for an account.


## Installation

Install the package directly from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("jdegregorio/ebaypi")
```


## Usage

```{r, message = FALSE}
library(ebaypi)

# Set token
set_ebay_token(keyring::key_get("ebay_api"))

# Make a search
df.items <- search_ebay(
  "babe ruth baseball card",
  type = "completed",
  item_filters = list(
    MinPrice = 50,
    MaxPrice = 10000
  )
)

tidyr::pivot_longer(df.items[1,], -rank, names_to = "attribute", values_to = "value")

```

## API Documentation

For complete API documention, please see the [eBay Developer API Webpage](https://developer.ebay.com/docs).

